Rank Recovery

### 2020-11-17 output_scripts/Paper_Plots.Rmd
add frob norm and structure score plots

library(here)
library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(bayesplot)
library(viridis)
library(compete)
library(colorspace)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source(paste(func_dir,'drawIntensity.R',sep =""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

@@

@@

```{r fig-8a-frob-norm-cohort5}
load("../output/plot_N_predict.RData")
# current_cohort <- 5# cohort 1 looks worse than rest

@@

```{r fig-pred-cor, eval=slides_plots,include=slides_plots,fig.height=3}
load("../output/plot_rank_predict.RData")
# current_cohort <- 5
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),width=600,height=300)
temp_plot_df <- temp_plot_df %>%
  filter(method != "I-MMHP") 
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #scale_fill_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
  #ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Rank correlation") +
  ylim(0, 1)
p5
```

@@

# current_cohort <- 5

>>>>

library(here)
library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(bayesplot)
library(viridis)
library(here)
library(compete)
library(colorspace)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source(paste(func_dir,'drawIntensity.R',sep =""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

@@

```{r fig-matrix-structure-score}
library(NMF)
source(here("lib","residualStructureScore.R"))

struct_scores <- tibble()
for(current_cohort in 1:10) {
  m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                   "/chp_pr_matrix_",cohort_names[current_cohort],
                   ".RDS",sep=''))
  ##
  ## remove animals which are never fought or don't ever fight
  prob_row <- which(rowSums(m1_pr) == 0)
  prob_col <- which(colSums(m1_pr) == 0)
  prob_id <- NA
  prob_id <- c(prob_row,prob_col)
  # print(prob_id)
  if(length(prob_id) != 0) {
    m1_pr <- m1_pr[-prob_id,-prob_id]
  }

  ##
  m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/dchp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))
  if(length(prob_id) != 0) {
    m2_pr <- m2_pr[-prob_id,-prob_id]
  }

  m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))
  if(length(prob_id) != 0) {
    m3_pr <- m3_pr[-prob_id,-prob_id]
  }
  indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/immhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))
  print(range(as.vector(indep_pr)))
  if(length(prob_id) != 0) {
    indep_pr <- indep_pr[-prob_id,-prob_id]
  }
  if(current_cohort == 10) {
    # one additional row
    # print("in here")
    new_prob_row <- which(rowSums(m1_pr) == 0)
    new_prob_col <- which(colSums(m1_pr) == 0)
    prob_id <- c(new_prob_row,new_prob_col) 
    if(length(prob_id) != 0) {
      m1_pr <- m1_pr[-prob_id, -prob_id]
      m2_pr <- m2_pr[-prob_id, -prob_id]
      m3_pr <- m3_pr[-prob_id, -prob_id]
      indep_pr <- indep_pr[-prob_id, -prob_id]
    }
  }

  m1_score <-positiveNegativeApproxError(m1_pr)
  m2_score <- positiveNegativeApproxError(m2_pr)
  m3_score <- positiveNegativeApproxError(m3_pr) ## smallest value which is good
  ind_score <- positiveNegativeApproxError(indep_pr) 
  ## this doesn't make sense because all negative
  ## values
  current_score <- tibble(m1_score, m2_score, m3_score, ind_score)
  names(current_score) <- c("C-HP","C-DCHP","C-MMHP","I-MMHP")
  current_score$type <- c("Positive","Negative")
  current_score$Cohort <- current_cohort
  struct_scores <-struct_scores %>% bind_rows(current_score)
}

struct_scores %>% 
  rename(Pos_Neg = type) %>%
  pivot_longer(cols = "C-HP":"I-MMHP",
               names_to = "Method", values_to = "Score") %>%
  filter(Score > 0) %>%
  filter(!(Method == "ind_score" & Pos_Neg == "Positive")) %>%
  ggplot(aes(Method,Score)) + geom_boxplot() +
  facet_wrap(~Pos_Neg) + theme_minimal()

@@

```{r fig-8a-frob-norm-cohort5}
load("../output/plot_N_predict.RData")
current_cohort <- 5# cohort 1 looks worse than rest

@@

```{r fig-pred-cor, eval=slides_plots,include=slides_plots,fig.height=3}
load("../output/plot_rank_predict.RData")
current_cohort <- 5
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),width=600,height=300)
temp_plot_df <- temp_plot_df %>%
  filter(method != "I-MMHP") 
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #scale_fill_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
  #ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Rank correlation") +
  ylim(0, 1)
p5
```

@@

current_cohort <- 5

### 2020-11-17 output_scripts/rank_recovery.Rmd
adding plots for fig 4 repeated with data simulated from m1 and m2
add frob norm and structure score plots

```{r load in sims, options}
sim_files <- list.files(here("output","rank_sims","sims_m3_dc_isi"))

@@

```{r truth_m3}
all_sims %>%
  group_by(truth, m3_dc) %>%
  count() %>%
  mutate(per = n/20) %>%
  arrange(-per)
```

@@

```{r truth isi}
all_sims %>%
  group_by(truth, isi) %>%
  count() %>%
  mutate(per = n/20) %>%
  arrange(-per)

@@

```{r analyse sims}
sim_files <- list.files(here("output","rank_sims","sims_m3_dc_isi"))

@@

How does this compare to the optimal score using only the test data.
```{r fit isi to test}
isi98(test_wl)
```

>>>>

```{r load in sims, options}
sim_files <- list.files(here("output", "rank_sims",
                             "sims_m3_dc_isi"))

@@

```{r truth_m3}
all_sims %>%
  group_by(truth, m3_dc) %>%
  count() %>%
  mutate(per = n/50) %>%
  arrange(-per)
```

@@

```{r truth isi}
all_sims %>%
  group_by(truth, isi) %>%
  count() %>%
  mutate(per = n/50) %>%
  arrange(-per)

@@

```{r analyse sims}
sim_files <- list.files(here("output", "rank_sims",
                             "sims_m3_dc_isi_sparse"))

@@

How does this compare to the optimal score using only the test data.
They agree in this instance.
```{r fit isi to test}
isi98(test_wl)
```
